### 2009-10-30 doc/manuals/user_interface/ui-job.tex
Broker name sync with the current broker loader name
Added brokers description as a separate file, other small fixes
client.xml was renamed to client.confg, correcting references. Please port to final.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsync [options]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{name}&explicitly select or reject a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-j, --joblist}&\textit{filename}&file where user's job information will be stored\\
   \texttt{-f, --force}& &don't ask for confirmation\\
%   \texttt{-m, --merge}& &merge the found jobs with the jobs already in the joblist\\
   \texttt{-T, --truncate}& &truncate the job list before synchronising\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options] [filename]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject (-) a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{-f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{-j, --joblist}&\textit{filename}&file where user's job information will be stored\\
%   \texttt{-D, --dryrun}&&add dryrun option to the job description\\
   \texttt{-x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
%   \texttt{-U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-b, --broker}&\textit{string}&select broker method (default is Random)\\
   \texttt{-n, --dolocalsandbox}& &store job descriptions in local sandbox (useful for eventual resubmission/migration)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
   Arguments:&&\\
   \texttt{filename}&&file describing the job(s) to be submitted\\
\end{longtable}

@@

Possible broker values for the option \verb#-b# are:
\begin{itemize}
 \item[\texttt{Random}] -- ranks targets randomly (default)
 \item[\texttt{FastestQueue}] -- ranks targets according to their queue length
% \item[\texttt{FastestCPU}] -- ranks targets according to CPU performance
 \item[\texttt{Data}] -- ranks target according the amount of megabytes of the
requested input files that are already in the computing resource’s cache.
% \item[\texttt{SampleBroker}] -- Ranks targets randomly (written in Python)
\end{itemize}

@@

\begin{shaded}
   \uicommand{arcstat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename}& file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about a site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-i, --indexurl}& \textit{url} &URL of an index service\\
   \texttt{-q, --queues}&&show information about clusters and queues\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-t, --timeout}& \textit{time}& timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of job IDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-o, --stdout}& & show the stdout of the job (default)\\
   \texttt{-e, --stderr}& & show the stderr of the job\\
   \texttt{-l, --gmlog}& & show the grid manager's error log of the job\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcget [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-D, --dir} & \textit{dirname} & download directory (the job directory will be created in this directory)\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arckill [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcclean [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-f, --force} & & removes the job ID from the local list even if the job is not found on the Grid\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

>>>>

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsync [options]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{name}&explicitly select or reject a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-j, --joblist}&\textit{filename}&file where user's job information will be stored\\
   \texttt{-f, --force}& &don't ask for confirmation\\
%   \texttt{-m, --merge}& &merge the found jobs with the jobs already in the joblist\\
   \texttt{-T, --truncate}& &truncate the job list before synchronising\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsub [options] [filename]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-c, --cluster}&\verb#[-]#\textit{url}&explicitly select or reject (-) a specific site\\
   \texttt{-i, --index}&\textit{url}&explicitly select or reject (-) a specific index server\\
   \texttt{-e, --jobdescrstring}&\textit{filename}&string describing the job to be submitted\\
   \texttt{-f, --jobdescrfile}&\textit{filename}&file describing the job to be submitted\\
   \texttt{-j, --joblist}&\textit{filename}&file where user's job information will be stored\\
%   \texttt{-D, --dryrun}&&add dryrun option to the job description\\
   \texttt{-x, --dumpdescription}&&do not submit -- dump transformed job description to stdout\\
%   \texttt{-U, --unknownattr}&&allow unknown attributes in the job description\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-b, --broker}&\textit{string}&select broker method (default is Random)\\
   \texttt{-n, --dolocalsandbox}& &store job descriptions in local sandbox (useful for eventual resubmission/migration)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
   Arguments:&&\\
   \texttt{filename}&&file describing the job(s) to be submitted\\
\end{longtable}

@@

\input{ui-brokers}

@@

\begin{shaded}
   \uicommand{arcstat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename}& file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about a site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-i, --indexurl}& \textit{url} &URL of an index service\\
   \texttt{-q, --queues}&&show information about clusters and queues\\
   \texttt{-l, --long}& & long format (extended information)\\
   \texttt{-t, --timeout}& \textit{time}& timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arccat [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of job IDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-o, --stdout}& & show the stdout of the job (default)\\
   \texttt{-e, --stderr}& & show the stderr of the job\\
   \texttt{-l, --gmlog}& & show the grid manager's error log of the job\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcget [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-i, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-D, --dir} & \textit{dirname} & download directory (the job directory will be created in this directory)\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arckill [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}& & show information about clusters\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-k, --keep}& & keep files on gatekeeper (do not clean)\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcclean [options] [job ...]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-a, --all}& & all jobs\\
   \texttt{-j, --joblist}& \textit{filename} & file containing a list of jobIDs\\
   \texttt{-c, --cluster}&\verb#[-]#textem{name}&explicitly select or reject a specific site (cluster)\\
   \texttt{-s, --status}& \textit{statusstr} &only select jobs whose status is \textit{statusstr}\\
   \texttt{-f, --force} & & removes the job ID from the local list even if the job is not found on the Grid\\
   \texttt{-t, --timeout}& \textit{time} & timeout for queries (default 20 sec)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
   Arguments:&&\\
   \texttt{job ...} && list of job IDs and/or jobnames\\
\end{longtable}

### 2009-10-30 doc/manuals/user_interface/ui-proxy.tex
arcsync, arcsub and chelonia fixed
client.xml was renamed to client.confg, correcting references. Please port to final.

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcproxy [options]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-P, --proxy}& \textit{path} & path to the proxy file\\
   \texttt{-C, --cert}& \textit{path} & path to the certificate file\\
   \texttt{-K, --key}& \textit{path} & path to the key file\\
   \texttt{-T, --cadir}& \textit{path} & path to the trusted certificate directory, only needed for VOMS client functionality\\
   \texttt{-V, --vomses}& \textit{path} & path to the VOMS server configuration file\\
   \texttt{-S, --voms}& \textit{voms[:command]} & Specify VOMS server (more than one VOMS server can be specified like this:\\
   & &--voms VOa:command1 --voms VOb:command2)\\
   & &:command is optional, and is used to ask for specific attributes(e.g. roles). Command options are:\\
   & &all -- put all of this DN's attributes into AC;\\
   & &list -- list all of the DN's attribute,will not create AC extension;\\
   & &/Role=yourRole -- specify the role, if this DN has such a role, the role will be put into AC\\
   & &/voname/groupname/Role=yourRole -- specify the VO,group and role; if this DN has such a role, the role will be put into AC\\
   \texttt{-G, --gsicom}& & use GSI communication protocol for contacting VOMS services\\
   \texttt{-O, --old}& & use GSI proxy (default is RFC 3820 compliant proxy)\\
   \texttt{-I, --info}& & print all information about this proxy. In order to show the Identity (DN without CN as suffix for proxy) of the certificate, the 'trusted certdir' is needed.\\
   \texttt{-U, --user}& \textit{string} & username for MyProxy server\\
   \texttt{-L, --myproxysrv}& \textit{URL} & URL of MyProxy server\\
   \texttt{-M, --myproxycmd}& \textit{PUT|GET} & command to MyProxy server. The command can be PUT and GET.\\
   & &PUT/put -- put a delegated credential to MyProxy server;\\
   & &GET/get -- get a delegated credential from MyProxy server, credential (certificate and key) is not needed in this case.\\
   \texttt{-c, --constraint}& \textit{string} & proxy constraints\\
   \texttt{-t, --timeout}& \textit{seconds} & timeout in seconds (default 20 seconds)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcslcs [options]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-S, --ur;}& \textit{URL} & URL of SLCS Service (e.g. https://127.0.0.1:60000/slcs)\\
   \texttt{-I, --idp}& \textit{URL} & the name of IdP (e.g. https://idp.testshib.org/idp/shibboleth)\\
   \texttt{-U, --user}& \textit{string} & User account to IdP\\
   \texttt{-P, --password}& \textit{string} & password for user accoutn to IdP\\
   \texttt{-Z, --keysize}& \textit{integer} & size of the private key, default is 1024\\
   \texttt{-K, --keypass}& \textit{} & passphrase for protecting the private key; if not set, the private key file will not be protected by the passphrase.\\
   \texttt{-L, --lifetime}& \textit{hours} & life time of the credential (hours)), starting with current time\\
   \texttt{-D, --storedir}& \textit{path} & store directory of the credential\\
   \texttt{-t, --timeout}& \textit{seconds} & timeout in seconds (default 20 seconds)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-c, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.xml)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
\end{longtable}

>>>>

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcproxy [options]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-P, --proxy}& \textit{path} & path to the proxy file\\
   \texttt{-C, --cert}& \textit{path} & path to the certificate file\\
   \texttt{-K, --key}& \textit{path} & path to the key file\\
   \texttt{-T, --cadir}& \textit{path} & path to the trusted certificate directory, only needed for VOMS client functionality\\
   \texttt{-V, --vomses}& \textit{path} & path to the VOMS server configuration file\\
   \texttt{-S, --voms}& \textit{voms[:command]} & Specify VOMS server (more than one VOMS server can be specified like this:\\
   & &--voms VOa:command1 --voms VOb:command2)\\
   & &:command is optional, and is used to ask for specific attributes(e.g. roles). Command options are:\\
   & &all -- put all of this DN's attributes into AC;\\
   & &list -- list all of the DN's attribute,will not create AC extension;\\
   & &/Role=yourRole -- specify the role, if this DN has such a role, the role will be put into AC\\
   & &/voname/groupname/Role=yourRole -- specify the VO,group and role; if this DN has such a role, the role will be put into AC\\
   \texttt{-G, --gsicom}& & use GSI communication protocol for contacting VOMS services\\
   \texttt{-O, --old}& & use GSI proxy (default is RFC 3820 compliant proxy)\\
   \texttt{-I, --info}& & print all information about this proxy. In order to show the Identity (DN without CN as suffix for proxy) of the certificate, the 'trusted certdir' is needed.\\
   \texttt{-U, --user}& \textit{string} & username for MyProxy server\\
   \texttt{-L, --myproxysrv}& \textit{URL} & URL of MyProxy server\\
   \texttt{-M, --myproxycmd}& \textit{PUT$|$GET} & command to MyProxy server. The command can be PUT and GET.\\
   & &PUT/put -- put a delegated credential to MyProxy server;\\
   & &GET/get -- get a delegated credential from MyProxy server, credential (certificate and key) is not needed in this case.\\
   \texttt{-c, --constraint}& \textit{string} & proxy constraints\\
   \texttt{-t, --timeout}& \textit{seconds} & timeout in seconds (default 20 seconds)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
\end{longtable}

@@

\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcslcs [options]}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
   Options:&&\\
   \texttt{-S, --ur;}& \textit{URL} & URL of SLCS Service (e.g. https://127.0.0.1:60000/slcs)\\
   \texttt{-I, --idp}& \textit{URL} & the name of IdP (e.g. https://idp.testshib.org/idp/shibboleth)\\
   \texttt{-U, --user}& \textit{string} & User account to IdP\\
   \texttt{-P, --password}& \textit{string} & password for user accoutn to IdP\\
   \texttt{-Z, --keysize}& \textit{integer} & size of the private key, default is 1024\\
   \texttt{-K, --keypass}& \textit{} & passphrase for protecting the private key; if not set, the private key file will not be protected by the passphrase.\\
   \texttt{-L, --lifetime}& \textit{hours} & life time of the credential (hours)), starting with current time\\
   \texttt{-D, --storedir}& \textit{path} & store directory of the credential\\
   \texttt{-t, --timeout}& \textit{seconds} & timeout in seconds (default 20 seconds)\\
   \texttt{-d, --debug}& \textit{debuglevel}&debug level is one of  FATAL, ERROR, WARNING, INFO, DEBUG or VERBOSE\\
   \texttt{-c, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}& & print version information\\
   \texttt{-h, --help}& & print help page\\
\end{longtable}

### 2009-10-30 doc/manuals/ws-quick-guide/ws-quick-guide.tex
Keep documentation up-to-date to the GLUE2 schema
client.xml was renamed to client.confg, correcting references. Please port to final.

To avoid providing credential information on command line it is possible to have
user configuration file with predefined values. Default location for this file
is \texttt{~/.arc/client.xml}. There is an example installed in
\verb|$ARC_LOCATION/share/doc/arc/client.xml|. Please edit before copying it
into your home directory.

@@

The configuration of the ARC Echo client is specified in an XML
file. The location of the configuration file is specified by the
environment variable \verb|$ARC_ECHO_CONFIG|. If there is no such
environment
variable, the configuration file is assumed to be \verb|echo_client.xml| in
the current working directory.

@@

Service information:
 Service Name: MINIMAL Computing Element
 Service Type: org.nordugrid.arex

>>>>

To avoid providing credential information on command line it is possible to have
user configuration file with predefined values. Default location for this file
is \texttt{~/.arc/client.conf}. There is an example installed in
\verb|$ARC_LOCATION/share/arc/examples/client.conf.example|. Please edit before copying it
into your home directory.

@@

%%% This does not seem to be correct. The echo client seems to use a normal INI client configuration. Some one please verify this...
%~ The configuration of the ARC Echo client is specified in an XML
%~ file. The location of the configuration file is specified by the
%~ environment variable \verb|$ARC_ECHO_CONFIG|. If there is no such
%~ environment
%~ variable, the configuration file is assumed to be \verb|echo_client.conf| in
%~ the current working directory.

@@

Service information:
 Service Name: MINIMAL Computing Element
 Service Type: org.nordugrid.execution.arex

### 2009-10-30 doc/tech_doc/sec/arc-security-documentation.tex
client.xml was renamed to client.confg, correcting references. Please port to final.

  -c, --conffile=filename      configuration file (default ~/.arc/client.xml)

@@

\textit{./arcslcs -S https://127.0.0.1:60000/slcs -I https://squark.uio.no/idp/shibboleth -U root -P aa1122 -D   ~/arc-0.9/src/clients/credentials -c client.xml}

@@

\begin{verbatim}
<ArcConfig> 
   <!-- change the paths below to the location of your user certs --> 
   <!-- here only trusted certificates are set. Because this arcslcs is 
   not supposed to have x509 credential before the samlsso profile has been 
   (by using client's username/password credential) passed and the SLCS 
   service succeeded to repond this client with the signed x509 credential. 
   On the SLCS service's configuration: ClientAuthn should be off.--> 
   <!--KeyPath>./testkey-nopass.pem</KeyPath--> 
   <!--CertificatePath>./testcert.pem</CertificatePath--> 
   <CACertificatesDir>./certificates</CACertificatesDir> 
   <SLCSURL>https://127.0.0.1:60000/slcs</SLCSURL> 
   <IdPname>https://squark.uio.no/idp/shibboleth</IdPname> 
   <Username>root</Username> 
   <Password>aa1122</Password> 
   <Keysize>1024</Keysize> 
   <Keypass>123456</Keypass> 
   <CertLifetime>24</CertLifetime> 
   <StoreDir>./</StoreDir> 
   <Debug>INFO</Debug> 
</ArcConfig> 
\end{verbatim}

@@

\textit{./arcslcs -S https://127.0.0.1:60000/slcs -I https://squark.uio.no/idp/shibboleth -U staff -P 123456 -D /home/wzqiang/arc-0.9/src/clients/credentials -c client.xml}

>>>>

  -z, --conffile=filename      configuration file (default ~/.arc/client.conf)

@@

\textit{./arcslcs -S https://127.0.0.1:60000/slcs -I https://squark.uio.no/idp/shibboleth -U root -P aa1122 -D   ~/arc-0.9/src/clients/credentials -z client.confg}

@@

\begin{verbatim}
[common]
keypath=./testkey-nopass.pem
certificatepath=./testcert.pem
cacertificatesdirectory=./certificates
slcsurl=https://127.0.0.1:60000/slcs
idpname=https://squark.uio.no/idp/shibboleth
username=root
password=aa1122
keysize=1024
keypass=123456
certlifetime=24
storedir=./
verbosity=INFO
\end{verbatim}

@@

\textit{./arcslcs -S https://127.0.0.1:60000/slcs -I https://squark.uio.no/idp/shibboleth -U staff -P 123456 -D /home/wzqiang/arc-0.9/src/clients/credentials -z client.conf}
